Iroko: Predictive Datacenter Congestion Control

### 2017-12-11 Documents/Report/implementation.tex
Intro changes.

In addition, we used the following Linux command:
\[$tc -s qdisc show dev <interface>$ \] 
where $<interface>$ is the current host we are polling from. Using the obtained text, we then applied regex expressions to collect the packet loss, packet overlimits, and interface queues. Each of these data provide further information to hint at the current state of the data center. Our goal was to eliminate dropped packets, and used this to help Iroko make rate-limiting decisions. Overlimit packets provides information on when a link goes over it’s allocated bandwidth, and adds a potentially useful feature for our controller to learn from. Interface queues provide Iroko with information on the queue length of the host, which measures how many packets are buffered to be processed.  These additional statistics we hoped would provide our controller enough data to make meaningful inferences of the appropriate bandwidth allocation to each host.

>>>>

In addition, we used the following Linux command:\\
\texttt{tc -s qdisc show dev <interface>}\\
where \texttt{<interface>} is the current host we are polling from. Using the 
obtained text, we then applied regex expressions to collect the packet loss, 
packet overlimits, and interface queues. Each of these data provide further 
information to hint at the current state of the data center. Our goal was to 
eliminate dropped packets, and used this to help Iroko make rate-limiting 
decisions. Overlimit packets provides information on when a link goes over it’s 
allocated bandwidth, and adds a potentially useful feature for our controller 
to learn from. Interface queues provide Iroko with information on the queue 
length of the host, which measures how many packets are buffered to be 
processed.  These additional statistics we hoped would provide our controller 
enough data to make meaningful inferences of the appropriate bandwidth 
allocation to each host.
